Draft-assinment1

### 2017-02-15 Draft-xuezhou-sjb.Rmd
Update Draft-xuezhou-sjb.Rmd

#Table of Contents
*1. Introduction
*2. Goal
*3. Dataset Preparation
*4. Objective
*5. Summary of variables
    *5.1 Individual variable summary
       *5.1.1 School
          *5.1.1.1 State
          *5.1.1.2 Predominant Degree
          *5.1.1.3 Control of Institution
       *5.1.2 Student Body
          *5.1.2.1 Percentage first-generation students
          *5.1.2.2 Number of applications
       *5.1.3 Cost 
          *5.1.3.1 Average net price for Title IV institutions(both public and private institutions)
          *5.1.3.2 Percentage of students who are financially independent
       *5.1.4 Financial Aid
          *5.1.4.1 Percentage of undergraduates who receive a Pell Grant
          *5.1.4.2 Percent of all federal undergraduate students receiving a federal student loan
          *5.1.4.3 The median debt for students who have completed
          *5.1.4.4 The median debt for students who have not completed
       *5.1.5 Earning
          *5.1.5.1 Median family income in real 2015 dollars
          *5.1.5.2 Earning after graduation
       *5.1.6 Repayment
          *5.1.6.1 3-year Repayment rate
          *5.1.6.2 3-year Default rate
*6. Relationship between variables
    *6.1 NPT4_COMBINE VS State
    *6.2 Debt VS Cost
    *6.3 Percentage of Pell Grant VS college type(CONTROL)
    *6.4 Percentage first-generation students VS Statu
    *6.5 family income with Pell Grant
    *6.6 cost and median debts with earning
    *6.7 default with earning
    *6.8 degree type vs. earning
    *6.9 predominant degree, control  and earning after 6 year of entry
    *6.10 predominant degree + control (count)
    *6.11 control + earning
*7. Comparison between variables
*8. Findings and Conclusion

>>>>

#Table of Contents
*1.Introduction
*2.Goal
*3.Dataset Preparation
*4.Objective
*5.Summary of variables
 *5.1 Individual variable summary
  *5.1.1 School
   *5.1.1.1 State
   *5.1.1.2 Predominant Degree
   *5.1.1.3 Control of Institution
  *5.1.2 Student Body
    *5.1.2.1 Percentage first-generation students
    *5.1.2.2 Number of applications
  *5.1.3 Cost 
    *5.1.3.1 Average net price for Title IV institutions(both public and private institutions)
    *5.1.3.2 Percentage of students who are financially independent
  *5.1.4 Financial Aid
    *5.1.4.1 Percentage of undergraduates who receive a Pell Grant
    *5.1.4.2 Percent of all federal undergraduate students receiving a federal student loan
    *5.1.4.3 The median debt for students who have completed
    *5.1.4.4 The median debt for students who have not completed
  *5.1.5 Earning
    *5.1.5.1 Median family income in real 2015 dollars
    *5.1.5.2 Earning after graduation
  *5.1.6 Repayment
    *5.1.6.1 3-year Repayment rate
    *5.1.6.2 3-year Default rate
*6.Relationship between variables
 *6.1 NPT4_COMBINE VS State
 *6.2 Debt VS Cost
 *6.3 Percentage of Pell Grant VS college type(CONTROL)
 *6.4 Percentage first-generation students VS Statu
 *6.5 family income with Pell Grant
 *6.6 cost and median debts with earning
 *6.7 default with earning
 *6.8 degree type vs. earning
 *6.9 predominant degree, control  and earning after 6 year of entry
 *6.10 predominant degree + control (count)
 *6.11 control + earning
*7. Comparison between variables
*8. Findings and Conclusion
